Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-14 GWLDCII.tex
got rid of the bad uses of the word take

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  \st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will take the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.  {\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken \st{at} {\color{violet} by?} vertex $b$, as otherwise $b$ would never be contributed by $p$. Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the \hlfix{same propagators have been assigned beforehand}{see above.}.  Finally, we also note that $m\geq_i b+1$.

@@

In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$. In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.  Thus $q\in S_i$ and so $f$ is a factor of $r_i$.

>>>>

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  \st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will assign the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.  {\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ contributes vertex $b$, as otherwise $b$ would never be contributed by $p$. Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the \hlfix{same propagators have been assigned beforehand}{see above.}.  Finally, we also note that $m\geq_i b+1$.

@@

In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$. In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.  Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
